
## 加载钻石数据集
钻石数据集在工作空间内被列为一个 'Promise'。这是 R 中的一个特殊对象，你需要在数据上运行一个命令，来完全加载数据集。尝试运行一个摘要。  summary(diamonds)

```{r}
library(ggplot2)  #必须先加载ggplot包
data("diamonds") # 加载钻石数据集，ggplot包自带该数据集
summary(diamonds)
```


## R 中自带一些数据集。你可以输入命令 data(DATA_SET_NAME) 来加载这些数据集。
## 使用？diamonds来了解关于钻石数据集的信息
```{r}
?diamonds
```

## 练习价格直方图
```{r}
qplot(x = price, data = diamonds)
ggsave('priceHistogram.png') #保存最后一个plot
summary(diamonds$price)  #计算price的统计数据
```

## 计算一定价格范围内的钻石数量
```{r}
sum(diamonds$price < 500)
sum(diamonds$price < 250)
sum(diamonds$price >= 15000)
```

## 对价格直方图做一些调整
```{r}
qplot(x = price, data = diamonds, binwidth = 100) + scale_x_continuous(limits = c(0, 10000), breaks = seq(0,10000,1000))

```

## 切工-价格直方图，按切工来划分
```{r}
qplot(x = price, data = diamonds,binwidth = 500) + facet_wrap(~cut, ncol = 3, scales = "free") #参数scales可以让y-axis不统一

```

## 按切工分析钻石价格
```{r}
by(diamonds$price, diamonds$cut, max)

by(diamonds$price, diamonds$cut, summary)
```

## 根据切工分类，计算每克拉钻价格
```{r}
price_per_carat <- 0.0
diamonds$price_per_carat <- diamonds$price / diamonds$carat

## 按切工分类计算
qplot(x=price_per_carat, data = diamonds, binwidth = 0.05) + 
  facet_wrap(~cut, ncol = 3, scales = "free") + 
  scale_x_log10()
```


## 按cut、clarity、color画出相应的箱线图
```{r}
qplot(x = clarity, y = price, 
      data = subset(diamonds, !is.na(clarity)), 
                    geom = 'boxplot') + coord_cartesian(ylim = c(0, 7500))

by(diamonds$price, diamonds$clarity, summary)
```

## 按 cut、clarity、color画出相应的箱线图
```{r}
qplot(x = cut, y = price, 
      data = subset(diamonds, !is.na(cut)), 
                    geom = 'boxplot') + coord_cartesian(ylim = c(0, 7500))

by(diamonds$price, diamonds$cut, summary)
```

## 按 cut、clarity、color 画出相应的箱线图
```{r}
qplot(x = color, y = price, 
      data = subset(diamonds, !is.na(color)), 
                    geom = 'boxplot') + coord_cartesian(ylim = c(0, 10000))

by(diamonds$price, diamonds$color, summary)
```

## 按color表示每克拉的箱线图
```{r}
qplot(x = color, y = price_per_carat, 
      data = subset(diamonds, !is.na(color)), 
                    geom = 'boxplot') + coord_cartesian(ylim = c(0, 7500))

by(diamonds$price_per_carat, diamonds$color, summary)
```


## carat频率多边形
```{r}

#diamonds$b <- 1 
#by(diamonds$b, diamonds$carat, sum)

ggplot(aes(x = carat), data = diamonds) + 
  geom_freqpoly(binwidth=0.01) + 
  scale_x_continuous(limits = c(0, 1.10), breaks = seq(0, 1.10, 0.1)) +
  xlab('carat') + 
  ylab('frequency') 

```


# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to download a data set of your choice
# and create 2-5 plots that make use of the techniques from Lesson 3.

# You might use a simple histogram, a boxplot split over a categorical variable,
# or a frequency polygon. The choice is yours!

# You can find a link to the Gapminder website in the Instructor Notes.

# Once you've completed your investigation, create a post in the discussions that includes:
#       1. any questions you answered, your observations, and summary statistics
#       2. snippets of code that created the plots
#       3. links to the images of your plots

# You can save images by using the ggsave() command.
# ggsave() will save the last plot created.
# For example...
#                  qplot(x = price, data = diamonds)
#                  ggsave('priceHistogram.png')

# ggsave currently recognises the extensions eps/ps, tex (pictex),
# pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

# Copy and paste all of the code that you used for
# your investigation, and submit it when you are ready.
# ====================================================================================

## 读取数据
```{r}
employ <- read.csv('indicator_t 15-24 employ.csv', sep = ';')   ## 读取数据
```

## 查看变量
```{r}
names(employ)
```

## 查看1991年的就业率
```{r}
summary(employ$X1991)

library("ggplot2")
qplot(x = X1998, data = employ)
```

## 1998年就业率的箱线图
```{r}
qplot(x = X1998, y = X1998, data = employ, geom = 'boxplot')
summary(employ$X1998)
```

## 计算China从1991年到2007年的就业率曲线，暂时不会，等学完了再重新看这部分
```{r}
employ$xy <- c(1:178)/10.0
employ$xy <- factor(employ$xy)
qplot(x = xy, y = X1998 , data = employ) + 
  geom_line()
```


















